Level-Set method on \texttt{p4est}

### 2015-06-19 paper/tex/introduction.tex
Small edits

The idea of using SFCs for parallel partitioning of Quad-/Octrees is not new in itself and has been used by many researchers. For instance, \texttt{Octor} \cite{Tu;OHallaron;Ghattas:05:Scalable-parallel-oc} uses a Morton curve (also known as Z-curve) for traversing the leaves of an Octree for indexing and load balancing and has been scaled up to 62,000 cores \cite{Burstedde;Ghattas;Gurnis;etal:08:Scalable-adaptive-ma}.
\texttt{Dendro} \cite{Sampath;Adavani;Sundar;etal:08:Dendro:-parallel-alg} is
an example of a so-called linear Octree code in which new algorithms are
introduced for parallel partitioning and the development of a parallel
geometric multigrid that has been scaled up to about 32,000 cores
\cite{Sampath;Biros:10:A-parallel-geometric}.
More recently, authors in
\cite{Burstedde;Wilcox;Ghattas:11:p4est:-Scalable-Algo} extended these ideas by
optionally allowing for a collection, or a ``forest'', of connected Octrees,
% that are connected through a common, potentially unstructured, hexahedral grid.
which is partitioned in parallel using a global Morton curve.
%
% \textcolor{red}{How about adding the p4est comments here ?}
%
% An implementation of these algorithms is publicly available
%
% provides a simple API for handling the grid.
The \texttt{p4est} library \cite{p4est-github} provides a publicly available
implementation of these algorithms that is equally efficient for a single tree
as well as multiple trees and has been shown to scale to more than
% 200,000 cores,
450,000 CPU cores \cite{IsaacBursteddeWilcoxEtAl15}.
In fact, the algorithms presented in this paper are implemented on top of
the \texttt{p4est} API using a single octree to represent the unit cube.
% In fact, the algorithms presented in this paper are implemented on top of the
% \texttt{p4est} library \cite{p4est-github} that is publicly available and
% provides a simple API for handling the grid.
%
% and we do not discuss any algorithm that is already covered in
% \cite{Burstedde;Wilcox;Ghattas:11:p4est:-Scalable-Algo}.
We also make use of the popular \texttt{PETSc}
\cite{Balay;Abhyankar;Adams;etal:14:PETSc-Web-page} library for linear algebra
and its parallel primitives, such as parallel ghosted vector and scatter/gather
operations, which simplifies the implementation.

>>>>

The idea of using SFCs for parallel partitioning of Quad-/Octrees is not new in itself and has been used by many researchers. For instance, \texttt{Octor} \cite{Tu;OHallaron;Ghattas:05:Scalable-parallel-oc} uses a Morton curve (also known as Z-curve) for traversing the leaves of an Octree for indexing and load balancing and has been scaled up to 62,000 cores \cite{Burstedde;Ghattas;Gurnis;etal:08:Scalable-adaptive-ma}.
\texttt{Dendro} \cite{Sampath;Adavani;Sundar;etal:08:Dendro:-parallel-alg} is
an example of a so-called linear Octree code in which new algorithms are
introduced for parallel partitioning and the development of a parallel
geometric multigrid that has been scaled up to about 32,000 cores
\cite{Sampath;Biros:10:A-parallel-geometric}.
More recently, authors in
\cite{Burstedde;Wilcox;Ghattas:11:p4est:-Scalable-Algo} extended these ideas by
optionally allowing for a collection, or a ``forest'', of connected Octrees,
% that are connected through a common, potentially unstructured, hexahedral grid.
which is partitioned in parallel using a global Morton curve.
%
% \textcolor{red}{How about adding the p4est comments here ?}
%
% An implementation of these algorithms is publicly available
%
% provides a simple API for handling the grid.
The \texttt{p4est} library \cite{p4est-github} provides a publicly available
implementation of these algorithms that is equally efficient for a single tree
as well as multiple trees and has been shown to scale to more than
% 200,000 cores,
450,000 CPU cores \cite{IsaacBursteddeWilcoxEtAl15}.
In fact, the algorithms presented in this paper are implemented on top of
the \texttt{p4est} API.
Due to the need for multiple adaptation and partitioning operations in each
time step, the semi-Lagrangian method we describe below presents a stringent
test of the algorithms and implementation both in terms of scalability and
absolute run time.
% using a single octree to represent the unit cube.
% In fact, the algorithms presented in this paper are implemented on top of the
% \texttt{p4est} library \cite{p4est-github} that is publicly available and
% provides a simple API for handling the grid.
%
% and we do not discuss any algorithm that is already covered in
% \cite{Burstedde;Wilcox;Ghattas:11:p4est:-Scalable-Algo}.

In implementing the numerical solver, we make use of the popular \texttt{PETSc}
\cite{Balay;Abhyankar;Adams;etal:14:PETSc-Web-page} library for linear algebra
and its parallel primitives, such as parallel ghosted vector and scatter/gather
operations, which simplifies the implementation.
